Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-19 Draft/Draft20181218.Rmd
.

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
date: "December 2018"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
    number_sections: false
    df_print: paged
    code_folding: hide

@@

treemap(pim1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Import Percentage on Countries",
        fontsize.title = 17,type="value",palette = "Set1")
```

@@

Besides this analysis, we can discover more on this topic with different perspectives. To do this, we decided to build up shiny app with dependents of Country, Product and Year. Please follow the link to access to Shiny app.
__[Link](https://groupfour.shinyapps.io/tradeOrg)__

@@

Please follow the link for interactive graph: __[Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)__

>>>>

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
date: "December 2018"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false
    df_print: paged
    code_folding: hide
    theme: journal
    #highlight: tango

@@

treemap(pim1_table,index = c("Country"),vSize = "perc_count",vColor = "perc_count",title="Total Import Percentage on Countries",
        fontsize.title = 17,type="value",palette = "Set1")

@@

Besides this analysis, we can discover more on this topic with different perspectives. To do this, we decided to build up shiny app with dependents of Country, Product and Year. Please follow the link to access to Shiny app. ***[Link](https://groupfour.shinyapps.io/tradeOrg)***

@@

Please follow the link for interactive graph: ***[Link](https://groupfour.shinyapps.io/tradeOrgProAnly/)***
